Hypoglycemia Analysis - CFRD REMOVED

### 2023-04-10 Christine Chan/Hypoglycemia/tim_analysis_no_CFRD.Rmd
Update tim_analysis_no_CFRD.Rmd
hypo +/- labels

table_dat$CF_hypo_60[table_dat$CF == "Yes" & table_dat$hypo_60 == "Yes"] <- "CF/Hypo"
table_dat$CF_hypo_60[table_dat$CF == "Yes" & table_dat$hypo_60 == "No"] <- "CF/No-Hypo"
table_dat$CF_hypo_60[table_dat$CF == "No" & table_dat$hypo_60 == "Yes"] <- "HC/Hypo"
table_dat$CF_hypo_60[table_dat$CF == "No" & table_dat$hypo_60 == "No"] <- "HC/No-Hypo"

table_dat$CF_hypo_70[table_dat$CF == "Yes" & table_dat$hypo_70 == "Yes"] <- "CF/Hypo"
table_dat$CF_hypo_70[table_dat$CF == "Yes" & table_dat$hypo_70 == "No"] <- "CF/No-Hypo"
table_dat$CF_hypo_70[table_dat$CF == "No" & table_dat$hypo_70 == "Yes"] <- "HC/Hypo"
table_dat$CF_hypo_70[table_dat$CF == "No" & table_dat$hypo_70 == "No"] <- "HC/No-Hypo"

@@

- matsuda now significant on ANOVA with Hypo < 60
- OGTT Category pairwise comparison CF/Hypo60 vs CF/No-Hypo60 now significant
- HOMA-IR pairwise comparison CF/Hypo60 vs HC/No-Hypo60 now significant
- CGM Avg Glucose pairwise comparison CF/No-Hypo60 vs HC/Hypo60 no longer significant
- CGM Avg Glucose pairwise comparison CF/No-Hypo60 vs HC/No-Hypo60 no longer significant
- CGM MAG CF/No-Hypo60 vs HC/Hypo60 now significant
- Matsuda and Homa-IR pairwise comparisons CF/Hypo70 vs HC/No-Hypo70 now significant
- Delta Glucagon pairwise comparison CF/No-Hypo70 vs HC/Hypo70 no longer significant
- CGM Avg Glucose pairwise comparison CF/No-Hypo70 vs HC/Hypo70 no longer significant
- CGM Avg Glucose pairwise comparison CF/No-Hypo70 vs HC/No-Hypo70 no longer significant
- %time over 140 pairwise comparison CF/Hypo70 vs CF/No-Hypo no longer significant

@@

## Table 1 by CF/Hypo < 60

@@

kbl(ptab, caption = "Pairwise p-values") %>%
  column_spec(2, background = 
                ifelse(ptab$`CF/Hypo vs CF/No-Hypo` < 0.05, "red", "white")) %>%
  column_spec(3, background = 
                na.fill(ifelse(ptab$`CF/Hypo vs HC/Hypo` < 0.05, 
                               "red", "white"), "white)")) %>%
  column_spec(4, background = 
                na.fill(ifelse(ptab$`CF/Hypo vs HC/No-Hypo` < 0.05, 
                               "red", "white"), "white)")) %>%
  column_spec(5, background = 
                na.fill(ifelse(ptab$`CF/No-Hypo vs HC/Hypo` < 0.05, 
                               "red", "white"), "white)")) %>%
  column_spec(6, background = 
                na.fill(ifelse(ptab$`CF/No-Hypo vs HC/No-Hypo` < 0.05, 
                               "red", "white"), "white)"))
```

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_60, color = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_60, color = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo")),
    color = "black",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo")),
    color = "black",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

## Table 1 by CF/Hypo < 70

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_70, color = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo")),
    color = "black",
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_70, color = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo")),
    color = "black",
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo")),
    color = "black",
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo")),
    color = "black",
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_60, color = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_60, color = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(4.5, 5),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(4.5, 5),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_70, color = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_70, color = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(4.5, 5),
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(4.5, 5),
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

>>>>

table_dat$CF_hypo_60[table_dat$CF == "Yes" & table_dat$hypo_60 == "Yes"] <- "CF/Hypo+"
table_dat$CF_hypo_60[table_dat$CF == "Yes" & table_dat$hypo_60 == "No"] <- "CF/Hypo-"
table_dat$CF_hypo_60[table_dat$CF == "No" & table_dat$hypo_60 == "Yes"] <- "HC/Hypo+"
table_dat$CF_hypo_60[table_dat$CF == "No" & table_dat$hypo_60 == "No"] <- "HC/Hypo-"

table_dat$CF_hypo_70[table_dat$CF == "Yes" & table_dat$hypo_70 == "Yes"] <- "CF/Hypo+"
table_dat$CF_hypo_70[table_dat$CF == "Yes" & table_dat$hypo_70 == "No"] <- "CF/Hypo-"
table_dat$CF_hypo_70[table_dat$CF == "No" & table_dat$hypo_70 == "Yes"] <- "HC/Hypo+"
table_dat$CF_hypo_70[table_dat$CF == "No" & table_dat$hypo_70 == "No"] <- "HC/Hypo-"

@@

- matsuda now significant on ANOVA with Hypo < 60
- OGTT Category pairwise comparison CF/Hypo60 vs CF/No-Hypo60 now significant
- HOMA-IR pairwise comparison CF/Hypo60 vs HC/No-Hypo60 now significant
- CGM Avg Glucose pairwise comparison CF/No-Hypo60 vs HC/Hypo60 no longer significant
- CGM Avg Glucose pairwise comparison CF/No-Hypo60 vs HC/No-Hypo60 no longer significant
- CGM MAG CF/No-Hypo60 vs HC/Hypo60 now significant
- Matsuda and Homa-IR pairwise comparisons CF/Hypo70 vs HC/No-Hypo70 now significant
- Delta Glucagon pairwise comparison CF/No-Hypo70 vs HC/Hypo70 no longer significant
- CGM Avg Glucose pairwise comparison CF/No-Hypo70 vs HC/Hypo70 no longer significant
- CGM Avg Glucose pairwise comparison CF/No-Hypo70 vs HC/No-Hypo70 no longer significant
- %time over 140 pairwise comparison CF/Hypo70 vs CF/Hypo- no longer significant

@@

## Table 1 by CF/Hypo+ < 60

@@

kbl(ptab, caption = "Pairwise p-values") %>%
  column_spec(2, background = 
                ifelse(ptab$`CF/Hypo- vs CF/Hypo+` < 0.05, "red", "white")) %>%
  column_spec(3, background = 
                na.fill(ifelse(ptab$`CF/Hypo+ vs HC/Hypo+` < 0.05, 
                               "red", "white"), "white)")) %>%
  column_spec(4, background = 
                na.fill(ifelse(ptab$`CF/Hypo+ vs HC/Hypo-` < 0.05, 
                               "red", "white"), "white)")) %>%
  column_spec(5, background = 
                na.fill(ifelse(ptab$`CF/Hypo- vs HC/Hypo+` < 0.05, 
                               "red", "white"), "white)")) %>%
  column_spec(6, background = 
                na.fill(ifelse(ptab$`CF/Hypo- vs HC/Hypo-` < 0.05, 
                               "red", "white"), "white)"))
```

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_60, color = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo+", "CF/Hypo-"), c("CF/Hypo+", "HC/Hypo-")),
    color = "black",
    y_position = c(45, 50),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_60, color = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo+", "CF/Hypo-")),
    color = "black",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo+", "CF/Hypo-"), c("CF/Hypo+", "HC/Hypo-")),
    color = "black",
    y_position = c(45, 50),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo+", "CF/Hypo-")),
    color = "black",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

## Table 1 by CF/Hypo+ < 70

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_70, color = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo+", "CF/Hypo-")),
    color = "black",
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_70, color = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo+", "CF/Hypo-")),
    color = "black",
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo+", "CF/Hypo-")),
    color = "black",
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo+", "CF/Hypo-")),
    color = "black",
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_60, color = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo+", "CF/Hypo-"), c("CF/Hypo+", "HC/Hypo-")),
    color = "black",
    y_position = c(45, 50),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_60, color = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo+", "CF/Hypo-"), c("CF/Hypo+", "HC/Hypo-")),
    color = "black",
    y_position = c(4.5, 5),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo+", "CF/Hypo-"), c("CF/Hypo+", "HC/Hypo-")),
    color = "black",
    y_position = c(45, 50),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo+", "CF/Hypo-"), c("CF/Hypo+", "HC/Hypo-")),
    color = "black",
    y_position = c(4.5, 5),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_70, color = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo+", "CF/Hypo-"), c("CF/Hypo+", "HC/Hypo-")),
    color = "black",
    y_position = c(45, 50),
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_70, color = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo+", "CF/Hypo-"), c("CF/Hypo+", "HC/Hypo-")),
    color = "black",
    y_position = c(4.5, 5),
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo+", "CF/Hypo-"), c("CF/Hypo+", "HC/Hypo-")),
    color = "black",
    y_position = c(45, 50),
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo+", "CF/Hypo-"), c("CF/Hypo+", "HC/Hypo-")),
    color = "black",
    y_position = c(4.5, 5),
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
